On The Impact of Atoms of Confusion in JavaScript Code

### 2022-07-25 3_Method.tex
Reviewed the abstract and intro to make thenm consistent with Sections 3 and 4.
Re-reviewed the text of the methodology section pertaning to the two experiments. Tried to remove the word survey from it.

\castor{We must have introduced the atoms before.}
The first experiment we perform uses a repeated measures, or within-subject, design~\cite{Keselman:2001:ARM}. This experiment is inspired by the work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, but targeting JavaScript instead of the C language, and including some methodological differences. It covers all the atom candidates analyzed in the work of Gopstein et al. that can be transposed to JavaScript and adds candidates that are specific to JavaScript.
%Overall, we select 24 atom candidates in the repeated measures study.

@@

% The design of the repeated measures study considers two treatments: the presence or absence of atom candidates within the programs.
To identify atom candidates, we start out by selecting every atom candidate from Gopstein's study that can also happen in JavaScript. That excludes atoms related to pointers and preprocessor directives. Furthermore, we conduct an informal search of programming forums, solutions to Code Golf~\footnote{https://codegolf.stackexchange.com/} problems, code style guidelines, and expert knowledge to identify new atom candidates. Overall, the repeated measures analyzes 24 atoms, 15 from the original study and 9 that are new and specific to JavaScript. Table~\ref{tab:atoms_replication} presents the complete list.

@@

The study is conducted by means of a web application. As part of this effort, we carried out an informal pilot whose main objectives were (i) to spot bugs in the application and in the data collection mechanism; (ii) to gain feedback from respondents about the user experience of the application; and (iii) to formulate an estimate about how long answering the survey would take on average. Based on the feedback of the participants of the pilot, we present only one obfuscated and one clean version of each atom candidate, to reduce to total time of the study and potentially increase participation.% Initially, our plan was to present two of each.

We organize the study in three sections. In the first one we present instructions and also a check button whose checking means users agree that all collected data will be used anonymously and solely for research purposes. The instructions explain how the survey works and asks them to dedicate their attention to it. We stress to participants the importance of not using any aids during the survey, such as online or console interpreters.

@@

We do not provide feedback about the time subjects take to answer each question. We also do not tell them whether their answers are correct or not. This aims at avoiding introducing bias for future respondents. Since we posted the survey on social media platforms, possible threats could have arisen if we gave respondents instant feedback.

@@

We posted the survey on the authors' social media platforms, on Brazilian CS departments' mailing lists, and on two programming subreddits. We explained our research purposes and asked developers to take the survey only if they have some familiarity with JavaScript. We collected 70 responses. %The average survey respondent has a mean 26 months of experience in JavaScript, with a median of 12.\castor{We should not say this here unless we are able to do the same for the Latin square study. }

@@

We implemented our survey as a web application and 
%carried out a pilot. 
%As part of this effort, we 
carried out an informal pilot whose main objectives were (i) to spot bugs in the application and in the data collection mechanism; (ii) to gain feedback from respondents about the user experience of the application; and (iii) to formulate an estimate about how long answering the survey would take on average.
Undergraduate students and professional colleagues took the pilot survey. Some users reported layout defects, and many reported that the landing page did not explain the survey well enough. We also spotted minor issues with our routines to create and populate the latin squares.

We organize the survey in three sections. The first section aims to characterize the subjects, asking their age, education level, and programming experience. We also include a check button, whose checking means users agree that all collected data will be used solely for research purposes. In the second section, we present to the participants a small set of instructions, where we explain how the survey works and ask them to dedicate their attention to it. We stress to participants the importance of not using any aids during the survey, such as online or console interpreters. For each question page, we kept track of whether or not the subjects switch windows.

The last section of the survey presents a sequence of ten questions, each containing a program. For each question, there is a text box where the answer should be written. There is also an ``I do not know'' button, which, when clicked, leads the subject to the next question. In our setting, ``I do not know'' is treated as a wrong answer. The programs are also presented as images copied from a text editor. Upon submitting their answer for a particular question, the subjects are automatically led to a similar page, containing another program. Similarly to the repeated measures study, we do not provide feedback about time and correctness to the subjects.

@@

We posted the survey on a JavaScript Reddit channel.\footnote{https://www.reddit.com/r/javascript/} We explained our research purposes and asked developers of any level of expertise to take the survey. Within twelve hours, we collected more than 150 answers, populating more than 70 replicas of the Latin Squares. We collected significant data on time taken and discrepancies in answer correctness between obfuscated and clean versions of the programs. Some inconsistencies arose while building the squares, for instance, when a user quit in the middle of the survey. We discarded from our study all squares that contained incomplete rows (a common approach for data imputation).
%Since we had a large enough number of samples, the squares we had to discard did not impact our analysis.

@@

\subsubsection*{Participant Selection} We invite the participants of the interviews using a snowballing technique. That is, starting from our network of contacts, we invite an initial set of candidates to take part in our survey. From this initial list, we ask for an indication of additional candidates. Our main selection criterion is that all participants should have been working with JavaScript in their daily professional activities. We invited a total of 17 developers, and 15 of them agreed to participate.   
%We conducted the interviews for a period of two weeks.

\subsubsection*{Interview Process} We conduct semi-structured interviews using a web conferencing software. We record all the interviews with the consent of the participants. On average, the interviews last 26.29 minutes, with the shortest one lasting 14.59 minutes and the longest one 43.06 minutes. Two of the researchers conduct the interviews, and a third one listens to all the recordings to cross-validate the collected data. The interviews have three main parts. In the first one, we ask the developers the following demographic information: name, email, gender, level of education, current job position, JavaScript experience in years, and other programming languages they have worked with. Table \ref{pinterview} summarizes this demographic information.

>>>>

\castor{We must have introduced the atoms before.}
The first experiment we perform uses a repeated measures, or within-subject, design~\cite{Keselman:2001:ARM}. This experiment is inspired by the work of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, but targeting JavaScript instead of the C language, and including some methodological differences. It covers all the atom candidates analyzed in the work of Gopstein et al. that can be transposed to JavaScript and adds candidates that are specific to this language.
%Overall, we select 24 atom candidates in the repeated measures study.

@@

% The design of the repeated measures study considers two treatments: the presence or absence of atom candidates within the programs.
To identify atom candidates, we start out by selecting every atom candidate from Gopstein's study that can also happen in JavaScript. That excludes atoms related to pointers and preprocessor directives. Furthermore, we conduct an informal search of programming forums, solutions to Code Golf~\footnote{https://codegolf.stackexchange.com/} problems, code style guidelines, and expert knowledge to identify new atom candidates. Overall, the repeated measures study analyzes 24 atoms, 15 from the original study and 9 that are new. Table~\ref{tab:atoms_replication} presents the complete list.

@@

The experiment is conducted by means of a questionnaire made available as a web application. As part of this effort, we carried out an informal pilot whose main objectives were (i) to spot bugs in the application and in the data collection mechanism; (ii) to gain feedback from respondents about the user experience of the application; and (iii) to formulate an estimate about how long answering the questionnaire would take on average. Based on the feedback of the participants of the pilot, we present only one obfuscated and one clean version of each atom candidate, to reduce to total time of the study and potentially increase participation.% Initially, our plan was to present two of each.

We organize the study in three sections. In the first one we present instructions and also a check button whose checking means users agree that all collected data will be used anonymously and solely for research purposes. The instructions explain how the study works and asks them to dedicate their attention to it. We stress to participants the importance of not using any aids during the experiment, such as online or console interpreters.

@@

We do not provide feedback about the time subjects take to answer each question. We also do not tell them whether their answers are correct or not. This aims at avoiding introducing bias for future respondents. Since we posted information about the study on social media platforms, possible threats could have arisen if we gave respondents instant feedback.

@@

We posted the link to the questionnaire on the authors' social media platforms, on Brazilian CS departments' mailing lists, and on two programming subreddits. We explained our research purposes and asked developers to take part in the study only if they have some familiarity with JavaScript. We collected 70 responses. %The average survey respondent has a mean 26 months of experience in JavaScript, with a median of 12.\castor{We should not say this here unless we are able to do the same for the Latin square study. }

@@

We implemented our experiment as a questionnaire in a web application and 
%carried out a pilot. 
%As part of this effort, we 
carried out an informal pilot.% whose main objectives were (i) to spot bugs in the application and in the data collection mechanism; (ii) to gain feedback from respondents about the user experience of the application; and (iii) to formulate an estimate about how long answering the survey would take on average.
Undergraduate students and professional colleagues took part in the pilot. Some users reported layout defects, and many reported that the landing page did not explain the study well enough. We also spotted minor issues with our routines to create and populate the latin squares.

We organize the questionnaire in three sections. The first section aims to characterize the subjects, asking their age, education level, and programming experience. We also include a check button, whose checking means users agree that all collected data will be used solely for research purposes. In the second section, we present to the participants a small set of instructions, where we explain how the study works and ask them to dedicate their attention to it. We stress to participants the importance of not using any aids during the experiment, such as online or console interpreters. For each question page, we kept track of whether or not the subjects switch windows.

The last section of the questionnaire presents a sequence of ten questions, each containing a program. For each question, there is a text box where the answer should be written. There is also an ``I do not know'' button, which, when clicked, leads the subject to the next question. In our setting, ``I do not know'' is treated as a wrong answer. The programs are also presented as images copied from a text editor. Upon submitting their answer for a particular question, the subjects are automatically led to a similar page, containing another program. Similarly to the repeated measures study, we do not provide feedback about time and correctness to the subjects.

@@

We posted the invitation to take part in the study on a JavaScript Reddit channel.\footnote{https://www.reddit.com/r/javascript/} We explained our research purposes and asked developers of any level of expertise to take part. Within twelve hours, we collected more than 150 answers, populating more than 70 replicas of the Latin Squares. We collected significant data on time taken and discrepancies in answer correctness between obfuscated and clean versions of the programs. Some inconsistencies arose while building the squares, for instance, when a user quit in the middle of the questionnaire. We discarded from our study all squares that contained incomplete rows (a common approach for data imputation).
%Since we had a large enough number of samples, the squares we had to discard did not impact our analysis.

@@

\subsubsection*{Participant Selection} We invite the participants of the interviews using a snowballing technique. That is, starting from our network of contacts, we invite an initial set of candidates to take part in our experiments. From this initial list, we ask for an indication of additional candidates. Our main selection criterion is that all participants should have been working with JavaScript in their daily professional activities. We invited a total of 17 developers, and 15 of them agreed to participate.   
%We conducted the interviews for a period of two weeks.

\subsubsection*{Interview Process} We conduct semi-structured interviews using web conferencing software. We record all the interviews with the consent of the participants. On average, the interviews last 26.29 minutes, with the shortest one lasting 14.59 minutes and the longest one 43.06 minutes. Two of the researchers conduct the interviews, and a third one listens to all the recordings to cross-validate the collected data. The interviews have three main parts. In the first one, we ask the developers the following demographic information: name, email, gender, level of education, current job position, JavaScript experience in years, and other programming languages they have worked with. Table \ref{pinterview} summarizes this demographic information.
